### 2019-09-25 reports/thesis/chapters/2_dataCollection.tex
Final revise

The test object is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The CAD model of the test sample is shown in Figure \ref{fig:inference_testObject}.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD model of the test sample; the scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

The \emph{Fortus 400mc (Stratasys, US)} was used to manufacture the test object made of plastic (acrylonitrile butadiene styrene or ABS). The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector. The target material in the x-ray tube was tungsten. The detector was made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produced a 16-bit projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}. Therefore, the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$. The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects. The gain and offset were adjusted by the engineers to produce a projection with good contrast and negligible penumbra effect. Each pixel has a grey value in units of analogue to digital units (\SI{}{\adu}).

Greyscale projections were taken in addition to the projection of the test object. These are projections with nothing between the source and the detector, obtained with the x-ray tube at different powers. The power was varied by fixing the potential difference and varying the current. The greyscale projections were used for calibration such as shading correction. The greyscale projection with the x-ray turned off is called the black image. The greyscale projection with the x-ray set up the same when obtaining the test sample projection is called the white image.

@@

A \SI{0.35}{\milli\metre} copper filter was used to tackle beam hardening.

\emph{aRTist} was used to simulate the test object projection and all greyscale projections except for the black image. The black image was simulated by producing a uniform image with a grey value the mean over the obtained black image. The engineers used numerical methods to align the simulated projection with the obtained projection.

@@

\begin{sidewaystable}
\centering
\begin{tabular}{l|cc}
                                                       & \multicolumn{2}{c}{Dataset name}                      \\
                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             \\ \hline
potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             \\
power (\SI{}{\watt})                                   & 36                   & 20                             \\
filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper \\
time exposure (\SI{}{\milli\second})                   & 708                  & 500                            \\
distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            \\
distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            \\
number of replications for each angle                  & 100                  & 20                             \\ \hline
powers used for greyscale projections (\SI{}{\watt})   & 0.0                  & 0.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 10                   & 5.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 18                   & 10                             \\
\multicolumn{1}{c|}{\vdots}                            & 28                   & 15                             \\
\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             \\
number of replications for each power                  & 20                   & 20                             
\end{tabular}
\caption{Properties of the two datasets obtained for the experiment.}
\label{table:data_dataset}
\end{sidewaystable}

@@

Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity, observed in the projections, as a result from panel effects, spot effects and other artefacts. Shading correction is done by using the greyscale projections and examining how the grey values respond to different powers for different pixels. For example, the black and white image can be used to correct the projections using
\begin{equation}
U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times B+A
\label{eq:data_shadingCorrectionOld}
\end{equation}
where $N_{x,y}$ is the obtained projection, $U_{x,y}$ is the shading corrected projection and $A$ and $B$ are some user defined constants \citep{young2000shading, munzenmayer2003enhancing}. This can be extended to include more greyscale projections by modelling the grey value to respond linearly to the power of the x-ray source \citep{seibert1998flat}. More generally, shading correction can be expressed as
\begin{equation}
U_{x,y} = \beta_{x,y} N_{x,y} + \alpha_{x,y}
\end{equation}
where $\alpha_{x,y}$ and $\beta_{x,y}$ are some spatially varying functions \citep{munzenmayer2003enhancing}. This model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ may depend on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}. Other methods include minimising the entropy of the projection while constraining $\alpha_{x,y}$ and $\beta_{x,y}$ to be some parametric function \citep{likar2000retrospective} and using a low pass filter to remove low spatial frequencies from the projections \citep{young2000shading, munzenmayer2003enhancing}.

@@

Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$. $S_{x,y}(P)$ may be averaged over replications. Let $x=1,2,3,\dotsc, W$ and $y=1,2,3,\dotsc,H$. Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$. The black and white image can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively. The power was varied by fixing the potential difference and varying the current of the x-ray tube.

@@

A variation of the shading correction which uses only the black and white image such that $\mathbb{P}=\left\{0, P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
  }
  \caption{Grey values in the greyscale projections before and after shading correction using the \texttt{AbsNoFilter} dataset. The box plot summarise all $2\,000\times2\,000$ pixels in a projection.}
  \label{fig:data_shadingCorrectionExample_greyvaluePower}
\end{figure}

@@

The BW shading corrected black and white image appeared uniform but there is some structure in the linear shading correction. By giving linear shading correction various greyscale projections, it attempts to generalise to a range of powers, thus may struggle at shading correcting the black and white images.

@@

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The box plots represent the 100 repeats. The \texttt{AbsNoFilter} dataset was used here.}
  \label{fig:data_anovaAbsNoFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The box plots represent the 100 repeats. The \texttt{AbsFilter} dataset was used here.}
  \label{fig:data_anovaAbsFilter}
\end{figure}

>>>>

The test sample is a cuboid (\SI{40.0}{\milli\metre} $\times$ \SI{40.0}{\milli\metre} $\times$ \SI{60.0}{\milli\metre}) with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The CAD model of the test sample is shown in Figure \ref{fig:inference_testObject}.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
  \caption{The CAD model of the test sample. The scale is approximate.}
  \label{fig:inference_testObject}
\end{figure}

The \emph{Fortus 400mc (Stratasys, US)} was used to manufacture the test sample made of plastic (acrylonitrile butadiene styrene or ABS). The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector. The target material in the x-ray tube was tungsten. A \SI{0.35}{\milli\metre} copper filter was used to tackle beam hardening. The detector was made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produced a 16-bit projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}. Therefore, the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$. The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects. The gain and offset were adjusted by the engineers to produce a projection with good contrast and negligible penumbra effect. Each pixel has a grey value in units of analogue to digital units (\SI{}{\adu}).

Greyscale projections were taken in addition to the projection of the test sample. These are projections with nothing between the source and the detector, obtained with the x-ray tube at different powers. The power was varied by fixing the potential difference and varying the current. The greyscale projections were used for calibration such as shading correction. The greyscale projection with the x-ray turned off is called the black image. The greyscale projection with the x-ray set up the same when obtaining the test sample projection is called the white image.

@@

\emph{aRTist} was used to simulate the test sample projection and all greyscale projections except for the black image. The black image was simulated by producing a uniform image with a grey value the mean over the obtained black image. The engineers used numerical methods to align the simulated projection with the obtained projection.

@@

\begin{sidewaystable}
\centering
\begin{tabular}{l|cc}
                                                       & \multicolumn{2}{c}{Dataset name}                      \\
                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             \\ \hline
potential difference (\SI{}{\kilo\volt}) of x-ray tube & 80                   & 80                             \\
power (\SI{}{\watt}) of x-ray tube                     & 36                   & 20                             \\
filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper \\
time exposure (\SI{}{\milli\second})                   & 708                  & 500                            \\
distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            \\
distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            \\
number of replications for each angle                  & 100                  & 20                             \\ \hline
powers used for greyscale projections (\SI{}{\watt})   & 0.0                  & 0.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 10                   & 5.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 18                   & 10                             \\
\multicolumn{1}{c|}{\vdots}                            & 28                   & 15                             \\
\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             \\
number of replications for each power                  & 20                   & 20                             
\end{tabular}
\caption{Properties of the two datasets obtained for the experiment.}
\label{table:data_dataset}
\end{sidewaystable}

@@

Shading correction, also known as flat field correction, aims to eliminate any spatial variation in sensitivity, observed in the projections, as a result from panel effects, spot effects and other artefacts. Shading correction is done by using the greyscale projections and examining how the grey values respond to different powers for different pixels. For example, the black and white images can be used to correct the projections using
\begin{equation}
U_{x,y} = \dfrac{N_{x,y}-\text{black}_{x,y}}{\text{white}_{x,y}-\text{black}_{x,y}}\times B+A
\label{eq:data_shadingCorrectionOld}
\end{equation}
where $N_{x,y}$ is the obtained projection, $U_{x,y}$ is the shading corrected projection and $A$ and $B$ are some user defined constants \citep{young2000shading, munzenmayer2003enhancing}. This can be extended to include more greyscale projections by modelling the grey value to respond linearly to the power of the x-ray source \citep{seibert1998flat}. More generally, shading correction can be expressed as
\begin{equation}
U_{x,y} = \beta_{x,y} N_{x,y} + \alpha_{x,y}
\end{equation}
where $\alpha_{x,y}$ and $\beta_{x,y}$ are some spatially varying functions \citep{munzenmayer2003enhancing}. This model has limitations because $\alpha_{x,y}$ and $\beta_{x,y}$ may depend on the energy of each photon, thus beam hardening could cause inaccuracies in shading correction \citep{davidson2003limitations}. Other methods include minimising the entropy of the projection while constraining $\alpha_{x,y}$ and $\beta_{x,y}$ to be some parametric function \citep{likar2000retrospective} and using a low pass filter to remove low spatial frequencies from the projections \citep{young2000shading, munzenmayer2003enhancing}.

@@

Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$. $S_{x,y}(P)$ may be averaged over replications. Let $x=1,2,3,\dotsc, W$ and $y=1,2,3,\dotsc,H$. Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$. The black and white images can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively. The power was varied by fixing the potential difference and varying the current of the x-ray tube.

@@

A variation of the shading correction which uses only the black and white images such that $\mathbb{P}=\left\{0, P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_power_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
  }
  \caption{Grey values in the greyscale projections before and after shading correction using the \texttt{AbsNoFilter} dataset. The boxplots summarise all $2\,000\times2\,000$ pixels in a projection.}
  \label{fig:data_shadingCorrectionExample_greyvaluePower}
\end{figure}

@@

The BW shading corrected black and white images appeared uniform but there is some structure in the linear shading correction. By giving linear shading correction various greyscale projections, it attempts to generalise to a range of powers, thus may struggle at shading correcting the black and white images.

@@

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The boxplots represent the 100 repeats. The \texttt{AbsNoFilter} dataset was used here.}
  \label{fig:data_anovaAbsNoFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The boxplots represent the 100 repeats. The \texttt{AbsFilter} dataset was used here.}
  \label{fig:data_anovaAbsFilter}
\end{figure}

### 2019-09-25 reports/thesis/chapters/3_compoundPoisson.tex
Revise and used proofreader
Final revise

Returning to the compound Poisson distribution with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$, let the moment generating function (m.g.f.) of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$. It can be shown that the m.g.f.~is
\begin{equation}
  M_X(\theta)=
  \exp\left[
    \lambda
    \left(
      M_U(\theta)-1
    \right)
  \right]
\end{equation}
\citep{gatto2010saddlepoint}. The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}. Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting $\theta$ to zero. In other words, $\expectation[X^r]=M_X^{(r)}(0)$. Then it can be shown that
\begin{align}
  \expectation\left[X\right]&=\lambda\expectation\left[U\right]
  \\
  \variance\left[X\right] &= \lambda\expectation\left[U^2\right]
  \\
  \expectation\left[(X-\expectation[X])^3\right] &=\lambda\expectation\left[U^3\right]
\end{align}
which agrees with the expectation and variance results in the previous section. The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}.

@@

Taking the derivative with respect to $\lambda$
\begin{equation}
  \frac{\partial T}{\partial\lambda} = -n + \frac{\sum_{i=1}^ny_i}{\lambda}
\end{equation}
and setting it to zero
\begin{equation}
  \widehat{\lambda} = \frac{\sum_{i=1}^n y_i}{n}
\end{equation}
obtains a M step estimator for $\lambda$. Taking the second derivative with respect to $\lambda$
\begin{equation}
  \frac{\partial^2 T}{\partial \lambda^2} = -\frac{\sum_{i=1}^ny_i}{\lambda^2} < 0
\end{equation}
verifies that $\widehat{\lambda}$ maximises $T$. In addition,
\begin{equation}
  \frac{\partial^2 T}{\partial \alpha \partial \lambda } = 0
\end{equation}
and
\begin{equation}
  \frac{\partial^2 T}{\partial \beta \partial \lambda } = 0
  \ .
\end{equation}

Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second-order can be obtained. For the first-order derivatives, these are:
\begin{multline}
  \frac{\partial T}{\partial \alpha} =
  \sum_{i=1}^n\mathbb{I}(x_i>0)
  \left[
    y_i\ln\beta -\psi(\alpha y_i)y_i-\zeta_i\alpha\psi'(\alpha y_i)
    \vphantom{\frac{1}{1}}
  \right.
  \\
  \left.
    - \frac{1}{2}\zeta_i\alpha^2\psi''(\alpha y_i)y_i + y_i\ln x_i
  \right]
\end{multline}
and
\begin{equation}
  \frac{\partial T}{\partial \beta} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
  \frac{\alpha y_i}{\beta}-x_i
  \right]
  \ .
\end{equation}
The second-order derivatives are
\begin{equation}
  \frac{\partial^2 T}{\partial \alpha \partial \beta} =
  \sum_{i=1}^n \mathbb{I}(x_i>0)\left[\frac{y_i}{\beta}\right]
  \ ,
  \label{eq:compoundPoisson:d2tdadb}
\end{equation}
\begin{equation}
  \frac{\partial^2 T}{\partial \beta^2} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[-\frac{\alpha y_i}{\beta^2}
  \right]
  \ ,
  \label{eq:compoundPoisson:d2td2b}
\end{equation}
and
\begin{multline*}
  \frac{\partial^2 T}{\partial \alpha^2} = 
  \sum_{i=1}^n\mathbb{I}(x_i>0)
  \left[
    -y_i^2\psi'(\alpha y_i) - \zeta_i\psi'(\alpha y_i) - \zeta_i\alpha y_i\psi''(\alpha y_i)
    \vphantom{\frac{1}{2}}\right.\\\left. 
    - \zeta_i\alpha\psi''(\alpha y_i)y_i
    -\frac{1}{2}\zeta_i\alpha^2\psi'''(\alpha y_i)y_i^2
  \right]
\end{multline*}
simplifying to
\begin{multline}
  \frac{\partial^2 T}{\partial \alpha^2} = 
  \sum_{i=1}^n\mathbb{I}(x_i>0)
  \left[
    -(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
    \vphantom{\frac{1}{2}}
  \right.
  \\
  \left.  
    -\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
  \right] \ .
  \label{eq:compoundPoisson:d2td2a}
\end{multline}

@@

The Fisher's information matrix is
\begin{multline}
  \matr{I}=
  n
  \left(\begin{matrix}
    \dfrac{1}{\lambda} & 0\\
    0 & \left(1-\euler^{-\lambda}\right)\left[(\lambda^2+\lambda)\psi'(\lambda\alpha)+2\lambda^2\alpha\psi''(\lambda\alpha)+\dfrac{\lambda^3\alpha^2}{2}\psi'''(\lambda\alpha)\right]\\
    0 & -\dfrac{\left(1-\euler^{-\lambda}\right)\lambda}{\beta}
  \end{matrix}\right.
  \\
  \left.\begin{matrix}
  \vphantom{\dfrac{1}{\lambda}}0\\
  -\dfrac{\left(1-\euler^{-\lambda}\right)\lambda}{\beta}\\
  \dfrac{\left(1-\euler^{-\lambda}\right)\alpha\lambda}{\beta^2}
  \end{matrix}\right)
  \ .
\end{multline}
The Cram\'er-Rao lower bound can be obtained using
\begin{equation}
  \cov\left[
    \begin{pmatrix}
      \widehat{\lambda}\\\widehat{\alpha}\\\widehat{\beta}
    \end{pmatrix}
  \right]
  =
  \matr{I}^{-1}
  \ .
\end{equation}

>>>>

Returning to the compound Poisson distribution with no electronic noise $X|Y = \sum_{i=1}^{Y}U_i$, let the moment generating function (m.g.f.)~of $X$ be $M_X(\theta)=\expectation\left[\euler^{X\theta}\right]$. It can be shown that the m.g.f.~is
\begin{equation}
  M_X(\theta)=
  \exp\left[
    \lambda
    \left(
      M_U(\theta)-1
    \right)
  \right]
\end{equation}
\citep{gatto2010saddlepoint}. The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}. Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting $\theta$ to zero. In other words, $\expectation[X^r]=M_X^{(r)}(0)$. Then it can be shown that
\begin{align}
  \expectation\left[X\right]&=\lambda\expectation\left[U\right]
  \\
  \variance\left[X\right] &= \lambda\expectation\left[U^2\right]
  \\
  \expectation\left[(X-\expectation[X])^3\right] &=\lambda\expectation\left[U^3\right]
\end{align}
which agrees with the expectation and variance results in the previous section. The derivation is shown in Appendix \ref{chapter:appendix_compoundPoissonMgf}.

@@

Taking the derivative with respect to $\lambda$
\begin{equation}
  \frac{\partial T}{\partial\lambda} = -n + \frac{\sum_{i=1}^ny_i}{\lambda}
\end{equation}
and setting it to zero
\begin{equation}
  \widehat{\lambda} = \frac{\sum_{i=1}^n y_i}{n}
\end{equation}
obtains a M step estimator for $\lambda$. Taking the second-order derivative with respect to $\lambda$
\begin{equation}
  \frac{\partial^2 T}{\partial \lambda^2} = -\frac{\sum_{i=1}^ny_i}{\lambda^2} < 0
\end{equation}
verifies that $\widehat{\lambda}$ maximises $T$. In addition,
\begin{equation}
  \frac{\partial^2 T}{\partial \alpha \partial \lambda } = 0
\end{equation}
and
\begin{equation}
  \frac{\partial^2 T}{\partial \beta \partial \lambda } = 0
  \ .
\end{equation}

Maximising $T$ with respect to $\alpha$ and $\beta$ can be done numerically using the Newton-Raphson method since derivatives up to the second-order can be obtained. For the first-order derivatives, these are
\begin{multline}
  \frac{\partial T}{\partial \alpha} =
  \sum_{i=1}^n\mathbb{I}(x_i>0)
  \left[
    y_i\ln\beta -\psi(\alpha y_i)y_i-\zeta_i\alpha\psi'(\alpha y_i)
    \vphantom{\frac{1}{1}}
  \right.
  \\
  \left.
    - \frac{1}{2}\zeta_i\alpha^2\psi''(\alpha y_i)y_i + y_i\ln x_i
  \right]
\end{multline}
and
\begin{equation}
  \frac{\partial T}{\partial \beta} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[
  \frac{\alpha y_i}{\beta}-x_i
  \right]
  \ .
\end{equation}
The second-order derivatives are
\begin{equation}
  \frac{\partial^2 T}{\partial \alpha \partial \beta} =
  \sum_{i=1}^n \mathbb{I}(x_i>0)\left[\frac{y_i}{\beta}\right]
  \ ,
  \label{eq:compoundPoisson:d2tdadb}
\end{equation}
\begin{equation}
  \frac{\partial^2 T}{\partial \beta^2} = \sum_{i=1}^n\mathbb{I}(x_i>0)\left[-\frac{\alpha y_i}{\beta^2}
  \right]
  \ ,
  \label{eq:compoundPoisson:d2td2b}
\end{equation}
and
\begin{multline*}
  \frac{\partial^2 T}{\partial \alpha^2} = 
  \sum_{i=1}^n\mathbb{I}(x_i>0)
  \left[
    -y_i^2\psi'(\alpha y_i) - \zeta_i\psi'(\alpha y_i) - \zeta_i\alpha y_i\psi''(\alpha y_i)
    \vphantom{\frac{1}{2}}\right.\\\left. 
    - \zeta_i\alpha\psi''(\alpha y_i)y_i
    -\frac{1}{2}\zeta_i\alpha^2\psi'''(\alpha y_i)y_i^2
  \right]
\end{multline*}
simplifying to
\begin{multline}
  \frac{\partial^2 T}{\partial \alpha^2} = 
  \sum_{i=1}^n\mathbb{I}(x_i>0)
  \left[
    -(y_i^2+\zeta_i)\psi'(\alpha y_i) - 2\zeta_i\alpha y_i\psi''(\alpha y_i)
    \vphantom{\frac{1}{2}}
  \right.
  \\
  \left.  
    -\frac{1}{2}\zeta_i\alpha^2y_i^2\psi'''(\alpha y_i)
  \right] \ .
  \label{eq:compoundPoisson:d2td2a}
\end{multline}

@@

Fisher's information matrix is
\begin{multline}
  \matr{I}=
  n
  \left(\begin{matrix}
    \dfrac{1}{\lambda} & 0\\
    0 & \left(1-\euler^{-\lambda}\right)\left[(\lambda^2+\lambda)\psi'(\lambda\alpha)+2\lambda^2\alpha\psi''(\lambda\alpha)+\dfrac{\lambda^3\alpha^2}{2}\psi'''(\lambda\alpha)\right]\\
    0 & -\dfrac{\left(1-\euler^{-\lambda}\right)\lambda}{\beta}
  \end{matrix}\right.
  \\
  \left.\begin{matrix}
  \vphantom{\dfrac{1}{\lambda}}0\\
  -\dfrac{\left(1-\euler^{-\lambda}\right)\lambda}{\beta}\\
  \dfrac{\left(1-\euler^{-\lambda}\right)\alpha\lambda}{\beta^2}
  \end{matrix}\right)
  \ .
\end{multline}
The Cram\'er-Rao lower bound can be obtained using
\begin{equation}
  \cov\left[
    \begin{pmatrix}
      \widehat{\lambda}\\\widehat{\alpha}\\\widehat{\beta}
    \end{pmatrix}
  \right]
  =
  \matr{I}^{-1}
  \ .
\end{equation}
